# Data Pre-processing

## Read data into R

The **National Chargepoint Register(NCR)** is a database of publicly-available chargepoints for electric vehicles in the UK established in 2011(,2021). you can access data in this [link](https://www.gov.uk/guidance/find-and-use-data-on-public-electric-vehicle-chargepoints#accessing-data-on-ncv)

Now, let's read original data in R
```{r,eval=FALSE}
UK_NCR= read.csv(here::here("dataset","national-charge-point-registry.csv")) 
# This may take for a while, which depends on the speed of internet

# you can have a overview of this dataset
print("The number of rows is: ")
nrow(UK_NCR)
print("The number of columns is: ")
ncol(UK_NCR)
print("70 of all varriables are:")
head(names(UK_NCR),n = 70)
```

Tip: If you cannot successfully read this dataset, you can replace the above link with "https://raw.githubusercontent.com/Hereislittlemushroom/CASA0005_Final_Assessment/main/Dataset/national-charge-point-registry.csv"

## Data Selection

Select the charge points of london area in this UK csv file。
You can utilise `filter` function from `dplyr` package to choose the charge point data in london boroughs

```{r,eval=FALSE}

London_NCR = UK_NCR %>%
  dplyr::filter(  !is.na(county),
                  county == "London" | 
                  county == "Greater London " | 
                  county == "London Borough of Camden" |
                  county == "London Borough of Ealing" | 
                  county == "London Borough of Greenwich" | 
                  county == "London Borough of Hackney" | 
                  county == "London Borough of Hammersmith and Fulham" | 
                  county == "London Borough of Hounslow" | 
                  county == "London Borough of Islington" | 
                  county == "London Borough of Lambeth" | 
                  county == "London Borough of Richmond upon Thames" | 
                  county == "London Borough of Southwark" |
                  county == "London Borough Of Southwark" |
                  county == "London Borough of Waltham Forest" | 
                  county == "London Borough of Wandsworth")
```

Check if all values in `county` are attributed to "London"
```{r,eval=FALSE}
isLondon = London_NCR$county %>%
  unique()
isLondon
```

In the next step, you can select the valuable attributes e.g. latitude,longitude.
```{r,eval=FALSE}
# Tip: the index of data frame starts from 1
# Select the variables by their index
London_NCR = London_NCR %>%
  select(1,4,5,13,14,15,32,35,36,38,54)

# Check the variables we have chosen and the number of rows & cols
London_NCR %>%
  names()
London_NCR %>%
  nrow()
London_NCR %>%
  ncol()
```

## Data Cleaning

Map and visualisation play important roles in spatial analysis. To make a heat map for further research, you need to merge geographic information for each row in charge point dataset in the first place.

To begin with, import "PostcodesioR". This R package offer methods to match
```{r,results='hide',eval=FALSE}
# install.packages("PostcodesioR")
library(PostcodesioR)
```

Before applying "for-loop" method to fill values in `GSS_CODE` by identifying `postcode`, you can add a new columns called `GSS_CODE` in London_NCR dataset.
```{r,eval=FALSE}
# Attentions: you can skip this chunk because the for-loop process can take for a quite long time (about 5 min).
# It is not necessary to stick on it, just skip!

London_NCR_GSS_Added = London_NCR %>%
  rowwise() %>%
  mutate(GSS_CODE = postcode) %>%
  # Tip: it is essential to transform numerical data into one in character
  mutate(GSS_CODE = as.character(GSS_CODE))

# Pay attention to the for loop in dataframe, it starts from 1

i = 1
for (val in London_NCR_GSS_Added$postcode) {
  try({ temp1 = PostcodesioR::postcode_lookup(val)
        if(!is.null(temp)){
          temp2 = temp1$admin_district_code[1]
          London_NCR_GSS_Added$GSS_CODE[i] = temp2
        }else{
          London_NCR_GSS_Added$GSS_CODE[i] = ""
        }
        i = i+1 }
      ,silent = TRUE)
}

# remove the rows whose value of `GSS_CODE` is empty
# There are limitations in this process because the rows missing `GSS_CODE` cannot be included in the dataset, which can slightly affect the research results 

London_NCR_GSS_Added$GSS_CODE[London_NCR_GSS_Added$GSS_CODE==""] = NA
London_NCR_GSS_Added = London_NCR_GSS_Added %>%
  filter(!is.na(GSS_CODE))
```

Finally, it is of importance to export our prepossessed data into csv file! Now we get the London_NCR_GSS_Added.csv in our "/Dataset" path. 

```{r,eval=FALSE}
# export London_NCR_GSS_Added data frame into .CSV format
library(here)
write.csv(London_NCR_GSS_Added, here::here("Dataset","London_NCR_GSS_Added.csv"), row.names = FALSE, col.names = TRUE)
# `col.names = TRUE` is important to be writen down
```
Also, you can access this prepocessed dataset in github link:
  https://raw.githubusercontent.com/Hereislittlemushroom/CASA0005_Final_Assessment/main/Dataset/London_NCR_GSS_Added.csv
