# Visualisation and comparison of the density of London EV charge point between two years

## Data cleaning for mapping

You should split the NCR dataset to two dataset of two years, and merged these two processed dataset with geometric data respectively. Then we calculate the density for two years. Finally we can visualise and map the density
   
```{r,results='hide'}
#5.1 process the data to divide them by years(2019 & 2020)
df1<-subset(df,year==2019) #2019 year
df2<-subset(df,year==2020) #2020 year

# EV charge points created in 2019
# sdf1<-merge(London_Borough,df1,by="GSS_CODE")
sdf1<-merge(London_Borough,df1,by="GSS_CODE",all = TRUE)
sdf1<-sdf1[,c("GSS_CODE","geometry","longitude","latitude")]

# EV charge points created in 2020
# sdf2<-merge(London_Borough,df2,by="GSS_CODE")
sdf2<-merge(London_Borough,df2,by="GSS_CODE",all = TRUE)
sdf2<-sdf2[,c("GSS_CODE","geometry","longitude","latitude")]

```

## The density of data in 2019

First, you should calculate the density and transform the unit of area from m^2 o km^2. Then, select the necessary columns and add frequency of samples grouped by `GSS_CODE`. In other words, you get the numeric and spatial data of EV charge point for each borough of London.
```{r,results='hide'}
# Data preparation
nsdf1 = sdf1%>%
  add_count(GSS_CODE)%>%
  mutate(area=st_area(.))%>%
  # Use dplyr::mutate to calculate the density of the charge point for each borough
  mutate(density=n*1000*1000/area)
  # because the st_area default unit is square metre

# select the following variables---"density","GSS_CODE","n"(the count of GSS_CODE)
nsdf1 = dplyr::select(nsdf1,density,GSS_CODE, n)

nsdf1 = nsdf1%>%                    
  group_by(GSS_CODE)%>%         
  summarise(density =first(density),GSS_CODE=first(GSS_CODE))
```

Now you can generate map after setting some variables in `tmap_mode`, `tm_compass` and `tm_polygons`.
```{r}
tmap_mode("plot")
# plot the figure: The distribution of the density of the London charge points in 2019
tm_shape( nsdf1) +
  tm_compass( north = 0,
              type = "4star",
              text.size = 0.8,
              size = 2.5,
              show.labels = 1,
              cardinal.directions = c("N", "E", "S", "W"),
              lwd = 1,
              position = c("left","top"),
              bg.color = NA,
              bg.alpha = NA,
              just = NA,
              fontsize = 1.5) +
  tm_polygons("density",
              style="jenks",
              palette="RdPu",
              midpoint=NA,
              popup.vars=c("GSS_CODE", "density"),
              title="Density per square kilometre (2019)"
              )
```
  
## The density of data in 2020

Then you should conduct the similar process as the 4.2 section to draw the density of EV charge point data in 2020.
```{r,results='hide'}
nsdf2 = sdf2%>%
  add_count(GSS_CODE)%>%
  mutate(area=st_area(.))%>%
  mutate(units::set_units(area,km^2))%>%
  mutate(density=n*1000*1000/area)

nsdf2 = dplyr::select(nsdf2,density,GSS_CODE, n)

nsdf2 = nsdf2%>%                    
  group_by(GSS_CODE)%>%         
  summarise(density =first(density),GSS_CODE=first(GSS_CODE))

tmap_mode("plot")
tm_shape( nsdf2) +
  tm_compass( north = 0,
              type = "4star",
              text.size = 0.8,
              size = 2.5,
              show.labels = 1,
              cardinal.directions = c("N", "E", "S", "W"),
              lwd = 1,
              position = c("left","top"),
              bg.color = NA,
              bg.alpha = NA,
              just = NA,
              fontsize = 1.5) +
  tm_polygons("density",
              style="jenks",
              palette="PuOr",
              midpoint=NA,
              popup.vars=c("GSS_CODE", "density"),
              title="Density per square kilometre (2020)")

```
