# Analysing Spatial Autocorrelation with Moran’s I
  
Since the sample in 2019 & 2020 is too small to run a good result, you can analysis the autocorrelation based on the samples which contain these two years.
  
## Generate the data for analysis

This process is similar to the 4.2 and 4.3 data preparation.
```{r,results='hide'}
sdf = merge(London_Borough,df,by="GSS_CODE",all = TRUE)
sdf = sdf[,c("GSS_CODE","geometry","longitude","latitude")]
nsdf = sdf%>%
  add_count(GSS_CODE)%>%
  mutate(area=st_area(.))%>%
  mutate(density=n*1000*1000/area)

nsdf = dplyr::select(nsdf,density,GSS_CODE, n)

nsdf = nsdf%>%                    
  group_by(GSS_CODE)%>%         
  summarise(density = first(density), GSS_CODE = first(GSS_CODE))
```

## Centroids and neighbour list

Plot the centroids of all boroughs in London
```{r}
coordsW = nsdf%>%
   st_centroid()%>%
   st_geometry()
 
 plot(coordsW,axes=TRUE)
```

Create a neighbours list

```{r}
 LWard_nb = nsdf %>% 
  poly2nb(.,queen=T)
```
 
Plot the neighbours list we create
```{r}
plot(nsdf$geometry)
plot(LWard_nb, st_geometry(coordsW), col="blue", add = T)
```

Create a spatial weights object from these weights, which can contribute to the further analysis autocorrelation analysis (Moran's I test)

```{r}
Lward.lw = nb2listw(LWard_nb, style="C")
head(Lward.lw$neighbours)
```

## Calculate the Global Moran'I Index
 
Conduct the global Moran's I test to get the value. 
```{r}
 I_LWard_Global_Density = nsdf %>%
   pull(density) %>%
   as.vector()%>%
   moran.test(.,Lward.lw)
names(I_LWard_Global_Density)
head(I_LWard_Global_Density)
```

Conduct the Local Moran's I test in these two years
```{r}
 I_LWard_Local_Density = nsdf %>%
   pull(density) %>%
   as.vector()%>%
   localmoran(., Lward.lw)%>%
   as_tibble()
```

Merge the moran test result with the geometric dataset. The I value is stored in "density_Iz" and the Z value is stored in "density_Iz".
```{r,results='hide'}
nsdf<-nsdf%>%
   mutate(density_I = as.numeric(I_LWard_Local_Density$Ii))%>%
   mutate(density_Iz =as.numeric(I_LWard_Local_Density$Z.Ii)) 
summary(nsdf$density_I)
summary(nsdf$density_Iz)
```

## Interactive visulisation of the distribution of the local Moran results

For drawing an interactive map, you should set "view" variables in `tmap_mode` function. You can set break box by the minimum and maximum value of Moran.
```{r}
tmap_mode("view")
#set the group and colour
summary(nsdf$density_Iz)
# breaks1 = seq(-3,1,0.5)
breaks1 = c(-2,-1,-0.1,-0.01,0,0.01,0.1,0.45,1,1.5 ) 
# breaks2 = c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
# Depends on the max and min value in Moran's I
MoranColours = rev(brewer.pal(8, "RdGy"))
# Plot the map
tm_shape(nsdf) +
  tm_polygons("density_Iz",
              style="fixed",
              breaks=breaks1,
              palette=MoranColours,
              midpoint=NA,
              title="Local Moran's I,EV charge points in London")

```

## GI score

You can repeat the similar process as you can in 5.4 section to do the data preparation.
```{r}
Gi_LWard_Local_Density = nsdf %>%
  pull(density) %>%
  as.vector()%>%
  localG(., Lward.lw)

# To get the Min and Max value
summary(Gi_LWard_Local_Density)
```
Calculate the Gi score and transform the data type into numeric one.
```{r}
Gi_nsdf = nsdf %>%
  mutate(density_G = as.numeric(Gi_LWard_Local_Density))
```

Based on the summary result of GI score to set the scale of breaks. Finally, the interactive map of Gi score distribution can be created.
```{r}
GIColours = rev(brewer.pal(8, "RdBu"))

# This breaks box bases on the summary result：
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# -0.8861 -0.4445 -0.1112  0.1998  0.4569  2.6561 
breaks_GI = c(-2,-1.5,-1,-0.4,-0.2,0,0.2,0.5,1,2,2.5,3)

# Now plot on an interactive map
tmap_mode("view")
tm_shape(Gi_nsdf) +
    tm_polygons("density_G",
        style="fixed",
        breaks=breaks_GI,
        palette=GIColours,
        midpoint=NA,
        title="Gi*, EV charge points in London")
```
